Figures

### 2020-03-03 figures/07_model-selection.Rmd
reorder figure 2 entries

```{r re-comparison, fig.width=4}
re_global <- dplyr::filter(re_global, term != "rowvcropvpct") %>%
mutate(signif = (`5%` > 0 & `95%` > 0)| (`5%` < 0 & `95%` < 0))

>>>>

```{r re-comparison, fig.width=4}
re_global <- dplyr::filter(re_global, term != "rowvcropvpct") %>%
mutate(signif = (`5%` > 0 & `95%` > 0)| (`5%` < 0 & `95%` < 0)) %>%
  mutate(term = factor(term, levels = c("wetlands", "forest", 
                                        "pasture", "soybeans", "corn", "ag")))
